Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-06-27 paper/revision/responseToReviewers.tex

\documentclass[10pt]{article}
\usepackage{url}

\title{Reply to reviewers concerning submission JASM-D-18-00019 "Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio"}

\begin{document}

\maketitle

As a preamble, we would like to thank the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

\section{Answer to Reviewer 1}

\begin{enumerate}

\item \emph{I understand that the authors cannot run such a test but I suggest that they only refer to ecoacoustics in the discussion by mentionning that this could be tested on other audio scenes as those recorded in natural environments.}

$\rightarrow$

\item \emph{The dataset is too quickly described. I had to read ref\#36 to understand how it was built and made of. It would be nice to have an example of a labelled recording either as a spectrogram or scalogram to estimate the complexity of the scenes recorded. The event classes should also be detailed.}

$\rightarrow$

\item \emph{It is a pity that the methods are not directly compared with the different strategies reported in ref\#36.}

$\rightarrow$

\item \emph{.P1L36: "superiority" and other superlative seems too strong. I would say that thet the proposed approach performed better on the dataset tested.}

$\rightarrow$

\item \emph{.P2L29: "cannot be trusted" seems too strong, any system is proned to errors. These errors need to be estimated so that we can estimate how much the system is reliable, but I would not roughly say that it cannot be trusted.}

$\rightarrow$

\item \emph{.P10L44: the title of this subsection does not seem to be totally appropriate, I would rename it "Evaluation and algorithm"}

$\rightarrow$

\item \emph{.P11L37: the comments about figure 3 (and others) is rather quick with no try of quantification of the differences/similarities between the p@k curves.}

$\rightarrow$

\item \emph{.P12L37: Delete the comment addressed to one of the authors}

$\rightarrow$

\item \emph{.P13L16: Using French for a project name might not be a good idea for reaching a large audience}

$\rightarrow$

\end{enumerate}

\section{Answer to Reviewer 2}

\begin{enumerate}

\item \emph{Only two applications are considered in the literature review, bioacoustics and urban sound environment, but they allow to present a problem that also exists in other application areas.}

$\rightarrow$

\item \emph{The authors present their technique as opposed to the BOF approach, that is considered "state of the art". BOF maybe a popular technique but the fact that gets rid of the temporal structure makes it useless in many tasks. In fact, in DCASE 2013 BOF was the chosen baseline system but no participant proposed that technique. Certainly, BOF allows the authors to make stronger the point about describing an acoustic scene from a few distinct events, but perhaps they should avoid to claim BOF as "the" state of the art in this problem.}

$\rightarrow$

\item \emph{It would be interesting to see the contribution to the results of the Gammatone wavelet in comparison to Morlet or another more classical wavelet.}

$\rightarrow$

\item \emph{There are several parameters that must be set in the experimentation. The reader may want to know if there is any specific parameter that is critical. What about M?}

$\rightarrow$

\item \emph{According to Section 6.2, the number of scattering features is much higher than MFCC features; 1367 instead of 40 for each vector, and there is a similar number of vectors per time unit. This would mean a much higher computational load. However, in the experiments, a projection is applied to reduce them to 30. Is it PCA? The convergence of the EM  algorithm is invoked, but the computational load may be an added reason.}

$\rightarrow$

\item \emph{I do not see the authors have mentioned in Section 7 the following observation (Fig.3): for MFCC the relevance-based quantization improves the performance wrt BOF.}

$\rightarrow$

\item \emph{Pag. 2, line 48: what "this" refers to?}

$\rightarrow$

\item \emph{Pag. 2, line 49: "More closely matches... than...}

$\rightarrow$

\item \emph{Pag. 3, line 22: an cluster -> a cluster}

$\rightarrow$

\item \emph{Pag. 3, line 23: Unconsistent sentence "These clusters to define..."}

$\rightarrow$

\item \emph{Equation (5): Notation is different from previous equations}

$\rightarrow$

\item \emph{Pag. 7, line 9: S1 should be S2}

$\rightarrow$

\item \emph{Pag. 9, line 48: suppress "the"}

$\rightarrow$

\end{enumerate}

\end{document}

### 2018-06-27 paper/lostanlenRelevanceScattering.tex
use endfloat
Address reviewer points 2.7-2.13

@@

\usepackage{stfloats}
% LaTeX2e). It also provides a command:
\fnbelowfloat

\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage[hyphens]{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

With this aim, we need to design an algorithm for acoustic similarity retrieval, where the audio fragments judged ``most similar'' to a given query recording must be extracted from some larger dataset. This requires us to represent an audio recording in a way that captures its distinctive qualities. This has previously been attempted using bag-of-frames approaches \cite{aucouturier2007bag}, which describes an auditory scene recording using summary statistics of short-time features. Unfortunately, this only captures the average structure of the scene, so the approach often fails when presented with highly dynamic scenes or those characterised by a few distinct sound events. Indeed, experiments in cognitive psychology \cite{dubois2006cognitive} and cognitive neuroscience \cite{nelken2004processing} suggest that this more closely matches human acoustic perception. We believe that the failure to model such distinct events is one of the reasons why this approach is insufficient for moderate-sized evaluation datasets \cite{lagrange:hal-01082501}.

@@

In this work, we propose a new model for acoustic scenes, where the signal is represented at sub-second scales by scattering transforms, while larger scales are captured by an cluster model. This unsupervised model quantizes the scattering coefficients into a given number of clusters. These clusters to define a set of distances for acoustic similarity retrieval. Evaluating this approach on a scene retrieval task, we obtain significant improvements over traditional bag-of-frames and summary statistics models applied both to MFCCs and scattering coefficients.

@@

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$. Consequently, they have central frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the following, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. Lastly, the low-pass filter $\boldsymbol{\phi}(t)$ is applied to $\boldsymbol{x_2}(t, \gamma_1, \gamma_2)$ to guarantee local invariance to time-shifting, which yields the second-order scattering coefficients
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \boldsymbol{\phi})(t).
\end{equation}

The scattering transform $\mathbf{S}\boldsymbol{x}(t,\gamma)$ consists of the concatenation of first-order coefficients $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)$ and second-order coefficients $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1,\gamma_2)$ into a feature matrix $\mathbf{S}\boldsymbol{x}(t,\gamma)$, where $\gamma$ denotes either $\gamma_1$ or $(\gamma_1,\gamma_2)$. While higher-order scattering coefficients can be calculated, for the purposes of our current work, the first and second order are sufficient.
Indeed, higher-order scattering coefficients have been shown to contain reduced energy and are therefore of limited use \cite{irene}.

@@

For \emph{RbQ-w}, each scene is represented by a signature
$$
p_u = \lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace,
$$
where each of the $M$ centroids $\mu_1^u, \ldots, \mu_M^u$ are paired with corresponding weights $w_1^u, \ldots, w_M^u$. The weight $w_m^u$ for the $m$th centroid $\mu_m^u$ is the number of frames belonging to a particular cluster. The similarity between scenes is then given by a cross-bin histogram distance known as the non-normalized earth mover's distance $\widehat{\EMD}$ introduced by \cite{pele2008linear}. The $\widehat{\EMD}$ computes the distance between two histograms by finding the minimal cost for transforming one histogram into the other, where cost is measured by the number of transported histogram counts multiplied by the a dissimilarity measure between the histogram bins. Here, that measure is given by $1-K_{mn}^{uv}$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_-1}
\end{center}
\end{figure}

>>>>

\usepackage[pagewise]{lineno}
\linenumbers

@@

\usepackage{stfloats}
% LaTeX2e). It also provides a command:
\fnbelowfloat
\usepackage{endfloat}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage[hyphens]{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

With this aim, we need to design an algorithm for acoustic similarity retrieval, where the audio fragments judged ``most similar'' to a given query recording must be extracted from some larger dataset. To construct such an algorithm, we are required to represent an audio recording in a way that captures its distinctive qualities. A popular choice of representation is the bag of frames \cite{aucouturier2007bag}, which describes an auditory scene recording using summary statistics of short-time features. Unfortunately, the bag-of-frames approach only captures the average structure of the scene, so the approach often fails when presented with highly dynamic scenes or those characterised by a few distinct sound events. Furthermore, experiments in cognitive psychology \cite{dubois2006cognitive} and cognitive neuroscience \cite{nelken2004processing} suggest that human acoustic perception is highly sensitive to such isolated sound events. We believe that the failure to model such distinct events is one of the reasons why the bag-of-frames representation is insufficient for moderate-sized evaluation datasets \cite{lagrange:hal-01082501}.

@@

In this work, we propose a new model for acoustic scenes, where the signal is represented at sub-second scales by scattering transforms, while larger scales are captured by a cluster model. This unsupervised model quantizes the scattering coefficients into a given number of clusters. These clusters are then used to define a set of distances for acoustic similarity retrieval. Evaluating this approach on a scene retrieval task, we obtain significant improvements over traditional bag-of-frames and summary statistics models applied both to MFCCs and scattering coefficients.

@@

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$. Consequently, they have central frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the following, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. Lastly, the low-pass filter $\boldsymbol{\phi}(t)$ is applied to $\boldsymbol{x_2}(t, \gamma_1, \gamma_2)$ to guarantee local invariance to time-shifting, which yields the second-order scattering coefficients
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \boldsymbol{\phi}(t).
\end{equation}

The scattering transform $\mathbf{S}\boldsymbol{x}(t,\gamma)$ consists of the concatenation of first-order coefficients $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)$ and second-order coefficients $\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2)$ into a feature matrix $\mathbf{S}\boldsymbol{x}(t,\gamma)$, where $\gamma$ denotes either $\gamma_1$ or $(\gamma_1,\gamma_2)$. While higher-order scattering coefficients can be calculated, for the purposes of our current work, the first and second order are sufficient.
Indeed, higher-order scattering coefficients have been shown to contain reduced energy and are therefore of limited use \cite{irene}.

@@

For \emph{RbQ-w}, each scene is represented by a signature
$$
p_u = \lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace,
$$
where each of the $M$ centroids $\mu_1^u, \ldots, \mu_M^u$ are paired with corresponding weights $w_1^u, \ldots, w_M^u$. The weight $w_m^u$ for the $m$th centroid $\mu_m^u$ is the number of frames belonging to a particular cluster. The similarity between scenes is then given by a cross-bin histogram distance known as the non-normalized earth mover's distance $\widehat{\EMD}$ introduced by \cite{pele2008linear}. The $\widehat{\EMD}$ computes the distance between two histograms by finding the minimal cost for transforming one histogram into the other, where cost is measured by the number of transported histogram counts multiplied by a dissimilarity measure between the histogram bins. Here, that measure is given by $1-K_{mn}^{uv}$.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for several baseline approaches, as a function of the rank $k$.}
\label{fig:ASS_-1}
\end{center}
\end{figure}
